Relationships in the extremes and their influence on competition and coexistence

### 2021-07-16 paper/Paper.Rnw
intro work

paragraph to inuitively explain storage effects
We emphasize that although this paper focuses on storage effects, it is still a paper generally about the importance of asymmetrical tail associations for coexistence because we do consider whether they are important for other mechanisms of modern coexistence theory, though we quickly realize their importance is solely for storage effects

[As we know], anthropogenic climate change has large consequences for almost all aspects of life including via extreme climatic events, which have only become more extreme - increasing in magnitude and frequency - and have contributed to both the increase in global means as well as an increase in environmental variability. 
There are many studies on the influence of environmental extremes and variability on competition and coexistence (Parepa et al 2013, Diez et al 2012); however, the study of the influence of relationships and interactions between drivers in their extremes on competition and coexistence, is lacking in the scientific literature. 
Interacting environmental drivers can be asymmetrically related in the extreme values (as shown in Gosh et al 2020 AER). Thus we have implemented our tools for the study ATAs to explore the importance of environmental relationships in their extremes on competition and coexistence. 
Environmental variability has been classically shown to promote coexistence via storage mechanisms in a lottery model of competition (Chesson and Warner 1981, Warner and Chesson 1985), hence we continue/move forward with this simple model to examine the effect of extreme relationships between environmental variables on the contribution of storage effects to coexistence.

@@

Results main ideas + example

introduce new decomposition

>>>>

For clarification, we explain the how storage effects operate in maintaining biodiversity and the conditions that are required for it to do so.
We emphasize that although this paper focuses on storage effects, we do consider other mechanisms of modern coexistence theory, though we quickly realize the importance of ATAs is solely for storage effects; hence, it is still a paper generally about the importance of ATAs for coexistence because. 
Storage effects allow for species to fluctuate over time while escaping extinction. 
In order for storage effect to be a functioning mechanism in coexistence, populations must fluctuate differently in response to environmental fluctuations, there must be a relationship between envrionmental responses and competition, and there must variation in responses at different life history stages. 
In a simple two species system, differences in environmental response allow for one species to grow to high densities while the other is very low. 
Competition is positively related to environmental response for the high density species (species A), stabalizing its growth. 
Conversely, competition is more negatively related to environmental response for the low density species (species B), leading to large fluctuations in population growth rate in both directions. 
Seemingly, this may appear like a scenario for extiction of species B, but it can, in fact, be at an advantage due to differences in life history stages. 
Different responses at different life stages buffer the species against extinction by limiting negative growth rates, but not positive ones. 
Examples of life stages that can buffering against negative growth rates are insensitive adults or dormant seeds that persist even when environmental response amoung others in the population is low (Chesson et al 2012). 
Thus, higher fluctuation in growth rate can lead to a higher long term mean growth rate. 
In this paper, we investigate the consequences of having ATAs in the relationship between fluctuations environmental response and competitive pressure. More specifically, we answer: Does having higher association in a tail end of the EC relationship, while maintaining overall association, change the contribution of storage effect?

[As we know], anthropogenic climate change threatens almost all aspects of life including via extreme climatic events, which have only become more extreme - increasing in magnitude and frequency - and have contributed to both the increase in global means as well as an increase in environmental variability. 
There are many studies on the influence of environmental extremes and variability on competition and coexistence (Parepa et al 2013, Diez et al 2012); however, the study of the influence of relationships and interactions between drivers in their extremes on competition and coexistence, is lacking in the scientific literature. 
Interacting environmental drivers can be asymmetrically related in the extreme values (as shown in Gosh et al 2020 AER). Thus we have implemented our tools for the study ATAs to explore the importance of environmental relationships in their extremes on competition and coexistence. 
Environmental variability has been classically shown to promote coexistence via storage mechanisms in a lottery model of competition (Chesson and Warner 1981, Warner and Chesson 1985), hence we continue/move forward with this simple model to examine the effect of extreme relationships between environmental variables on the contribution of storage effects to coexistence.

@@

(establish criteria for storage effects and establish connection to extreme events to introduce example)
Results main ideas + example

Previously, storage effects were described as the contribution of covariance between the environment and competition to coexistence (Chesson et al 2012, Ellner et al 2016, Ellner at al 2019). 
However, the description of storage effects as the covariance between drivers is a (potentially dangerous/irresponsible?) misnomer in terminology, and we argue that storage effects, instead, should be described as the contribution of the relationship between drivers. 
All aspects and contributing values of the relationship between environmental response and competitive pressure are not fully captured by only the covariance between them because a measure of covariance does not capture the strucutre of associativity throuhgout the distribution of the relationship and any asymmetries there may be. 
Thus, following the decomposition presented in Ellner et al (2019), we propose storage effect can be broken down further into the contribution of ATAs [to storage effect/coexistence] and the contribution of symmetric association [to storage effect/coexistence].
